EuringPosterFigures

### 2021-04-28 scripts/EuringPosterFigures.Rmd
case study figures added, changed color palette to something bolder

@@

#just bias
rel.bias <- all.meds %>%
  #calculate relative bias, mean across scenarios
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true) %>%
  dplyr::select('lambda.scenario', 'scenario', 'simscenarios', 
                'phi1.bias', 'phiad.bias', 'fec.bias') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'simscenarios')) %>%
  group_by(lambda.scenario, simscenarios, variable) %>%
  dplyr::summarize(mean.rel.bias = mean(value), .groups = 'keep') %>%
  transform(simscenarios = factor(simscenarios, levels = c(1:9), 
                                  labels = rep(c('L', 'M', 'H'), 3)))

# set factor levels
rel.bias$lambda.scenario <- factor(rel.bias$lambda.scenario, levels = c("Decreasing", "Stable", "Increasing"))

# plot
ggplot(rel.bias, aes(x = factor(simscenarios), y = variable, fill = mean.rel.bias)) +
  geom_tile() +
  xlab('Detection level') + ylab('') +
  facet_grid(~lambda.scenario, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
  theme_minimal() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

@@

#for the love of buddha, someone please check this calculation of rmse
rmse.vals <- all.meds %>%
  transform(rmse.fec = (fec.obs-fec.true)^2,
            rmse.phiad = (phiad.obs-phiad.true)^2,
            rmse.phi1 = (phi1.obs-phi1.true)^2) %>%
  dplyr::select(lambda.scenario, scenario, simscenarios, rmse.fec, rmse.phiad, rmse.phi1) %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'simscenarios')) %>%
  group_by(simscenarios, lambda.scenario, variable) %>%
  dplyr::summarize(rmse = sqrt(mean(value)), .groups = 'keep') %>%
  transform(simscenarios = factor(simscenarios, levels = c(1:9), 
                                  labels = rep(c('L', 'M', 'H'), 3)))

#dunno about this - looks suspiciously similar across detection levels :(
ggplot(rmse.vals, aes(x = factor(simscenarios), y = variable, fill = rmse)) +
  geom_tile() +
  xlab('Detection level') + ylab('') +
  facet_grid(~lambda.scenario, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "RMSE",
                      mid = "#FFFFFF", low = "#012345", high = "#012345", midpoint = 0) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

@@

```{r not using but keep for now}

### Keep to look at difference in bias across scenarios
# #get posterior medians
# low.meds <- low.dat %>%
#   dplyr::select('phi1.obs', 'phi1.true', 'phiad.obs', 'phiad.true', 'fec.obs', 'fec.true',
#                             'sims', 'scenario', 'simscenarios') %>%
#   reshape2::melt(id.vars = c('sims', 'scenario', 'simscenarios')) %>%
#   group_by(scenario, simscenarios, variable) %>%
#   summarize(median = median(value)) %>%
#   reshape2::dcast(scenario + simscenarios ~ variable, value.var = 'median') %>%
#   #calculate relative bias
#   transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true, 
#             phiad.bias = (phiad.obs-phiad.true)/phiad.true, 
#             fec.bias = (fec.obs-fec.true)/fec.true)
# 
# #just bias
# low.bias <- low.meds %>%
#   dplyr::select('scenario', 'simscenarios', 'phi1.bias', 'phiad.bias', 'fec.bias') %>%
#   reshape2::melt(id.vars = c('scenario', 'simscenarios')) %>%
#   transform(simscenarios = factor(simscenarios, labels = c('lam = low; p=L', 'M', 'H')))
# 
# ggplot(low.bias, aes(x = factor(scenario), y = variable, fill = value)) +
#   geom_tile() +
#   xlab('Scenario') + ylab('Parameter') +
#   facet_grid(~simscenarios, drop = T, scales = 'free_x') +
#   scale_fill_gradient2(name = "Relative bias",
#                       mid = "#FFFFFF", low = "#012345", high = "#012345", midpoint = 0) +
#   theme_bw() +
#   theme(legend.position = 'top',
#              strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

@@

>>>>

```{r process data}

@@

#just bias
rel.bias <- all.meds %>%
  #calculate relative bias, mean across scenarios
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true) %>%
  dplyr::select('lambda.scenario', 'scenario', 'simscenarios', 
                'phi1.bias', 'phiad.bias', 'fec.bias') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'simscenarios')) %>%
  group_by(lambda.scenario, simscenarios, variable) %>%
  dplyr::summarize(mean.rel.bias = mean(value), .groups = 'keep') %>%
  transform(simscenarios = factor(simscenarios, levels = c(1:9), 
                                  labels = rep(c('L', 'M', 'H'), 3))) %>%
  transform(variable = factor(variable, levels = c('phiad.bias', 'phi1.bias', 'fec.bias'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity'))) %>% 
  transform(lambda.scenario = factor(lambda.scenario, 
                                     levels = c("Decreasing", "Stable", "Increasing")))

# plot
ggplot(rel.bias, aes(x = factor(simscenarios), y = variable, fill = mean.rel.bias)) +
  geom_tile(color = 'grey50') +
  xlab('Detection level') + ylab('') +
  facet_grid(~lambda.scenario, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                     mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
  theme_minimal() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

@@

#for the love of buddha, someone please check this calculation of rmse
rmse.vals <- all.meds %>%
  transform(fec.rmse = (fec.obs-fec.true)^2,
            phiad.rmse = (phiad.obs-phiad.true)^2,
            phi1.rmse = (phi1.obs-phi1.true)^2) %>%
  dplyr::select(lambda.scenario, scenario, simscenarios, fec.rmse, phiad.rmse, phi1.rmse) %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'simscenarios')) %>%
  group_by(simscenarios, lambda.scenario, variable) %>%
  dplyr::summarize(rmse = sqrt(mean(value)), .groups = 'keep') %>%
  transform(simscenarios = factor(simscenarios, levels = c(1:9), 
                                  labels = rep(c('L', 'M', 'H'), 3))) %>%
  transform(variable = factor(variable, levels = c('phiad.rmse', 'phi1.rmse', 'fec.rmse'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity'))) %>% 
  transform(lambda.scenario = factor(lambda.scenario, 
                                     levels = c("Decreasing", "Stable", "Increasing")))

#dunno about this - looks suspiciously similar across detection levels :(
ggplot(rmse.vals, aes(x = factor(simscenarios), y = variable, fill = rmse)) +
  geom_tile(color = 'grey50') +
  xlab('Detection level') + ylab('') +
  facet_grid(~lambda.scenario, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "RMSE",
                      mid = "#FFFFFF", low = "#012345", high = "#012345", midpoint = 0) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

@@

```{r bias across life history scenarios}

##Same as above but looking at the variability across data-generating true values for phiad, phi1, fec

#get posterior medians; same as above except keep 'scenario' in group_by
all.meds.sc <- all.dat %>%
  dplyr::select('phi1.obs', 'phi1.true', 'phiad.obs', 'phiad.true', 'fec.obs', 'fec.true',
                            'sims', 'scenario', 'simscenarios', 'lambda.scenario') %>%
  reshape2::melt(id.vars = c('sims', 'scenario', 'simscenarios', 'lambda.scenario')) %>%
  group_by(lambda.scenario, scenario, simscenarios, variable) %>%
  summarize(median = median(value)) %>%
  reshape2::dcast(lambda.scenario + scenario + simscenarios ~ variable, value.var = 'median') %>%
  #calculate relative bias
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true)

#just bias; same as above, keep 'scenario'
rel.bias.sc <- all.meds.sc %>%
  dplyr::select('lambda.scenario', 'scenario', 'simscenarios', 
                'phi1.bias', 'phiad.bias', 'fec.bias') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'simscenarios')) %>%
  transform(simscenarios = factor(simscenarios, labels = rep(c('L', 'M', 'H'),3)))

#grab true values from above
true_vals <- all.dat %>%
  distinct(lambda.scenario, scenario, phiad.true, fec.true, phi1.true) %>%
  transform(phiad.true = round(phiad.true,1),
            phi1.true = round(phi1.true,1), fec.true = round(fec.true,1))

#for categories: 
fec_lims <- quantile(true_vals$fec.true, probs = c(0.33, 0.7), names = F)
phiad_lims <- quantile(true_vals$phiad.true, probs = c(0.33, 0.7), names = F)
phi1_lims <- quantile(true_vals$phi1.true, probs = c(0.33, 0.7), names = F)

#merge back onto bias df so can have something to name/view the 'scenarios' 
rel.bias.vals <- rel.bias.sc %>%
  merge(true_vals, by = c('lambda.scenario', 'scenario')) %>%
  transform(variable = factor(variable, levels = c('phiad.bias', 'phi1.bias', 'fec.bias'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity'))) %>% 
  transform(lambda.scenario = factor(lambda.scenario, 
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(fec_cat = ifelse(fec.true < fec_lims[1], 'L', ifelse(fec.true > fec_lims[2], 'H', 'M')),
            phiad_cat = ifelse(phiad.true < phiad_lims[1], 'L', ifelse(phiad.true > phiad_lims[2], 'H', 'M')),
            phi1_cat = ifelse(phi1.true < phi1_lims[1], 'L', ifelse(phi1.true > phi1_lims[2], 'H', 'M'))) %>%
  transform(fec_cat = factor(fec_cat, levels = c('L', 'M', 'H')),
            phiad_cat = factor(phiad_cat, levels = c('L', 'M', 'H')),
            phi1_cat = factor(phi1_cat, levels = c('L', 'M', 'H')))

#scenario number -- not a very useful view, but inspired this investigation
ggplot(rel.bias.sc, aes(x = factor(scenario), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('Scenario') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,

                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

#view by fec.true vals; 
ggplot(rel.bias.vals, aes(x = factor(fec.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True fecundity') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

#view by fec category: have to re-summarize to get mean across fec/phi ifelse categories
fec.plot.vals <- rel.bias.vals %>%
  group_by(lambda.scenario, simscenarios, variable, fec_cat) %>%
  dplyr::summarize(value = mean(value), .groups = 'keep')

ggplot(fec.plot.vals, aes(x = factor(fec_cat), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True fecundity') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

#view by phiad.true
ggplot(rel.bias.vals, aes(x = factor(phiad.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True phi.ad') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

#view by phiad category
phiad.plot.vals <- rel.bias.vals %>%
  group_by(lambda.scenario, simscenarios, variable, phiad_cat) %>%
  dplyr::summarize(value = mean(value), .groups = 'keep')

ggplot(phiad.plot.vals, aes(x = factor(phiad_cat), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Adult survival') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

#view by phi1.true
ggplot(rel.bias.vals, aes(x = factor(phi1.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True phi.1') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

#view by phi1 category
phi1.plot.vals <- rel.bias.vals %>%
  group_by(lambda.scenario, simscenarios, variable, phi1_cat) %>%
  dplyr::summarize(value = mean(value), .groups = 'keep')

ggplot(phi1.plot.vals, aes(x = factor(phi1_cat), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Juv survival') + ylab('Parameter') +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.5, -0.25, 0, 0.25, 0.5), n.breaks = 5, 
                      labels = c('0.5', "-0.25", "0", "0.25", '0.5')) +
  theme_bw() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

@@

### Case study
```{r load results from case study}

load(file = here::here('results', 'EuringPoster', 'processedIPMcasestudy.RData'))

#only decreasing population trend for now
# unique(row.low.cs$sims) #sims = 1:25 (sim repetitions); 
# unique(row.low.cs$scenario) #scenarios = 1:10 (phi/fec true vals);
# unique(row.low.cs$simscenarios) #simscenarios = 1:9 (...?)
row.low.cs <- do.call(rbind, lapply( ls(patt='lowout'), get) )
#remove interim rds files
rm(list=grep('highout|medout|lowout',ls(),value=TRUE,invert=FALSE))

#list of survey detection scenarios
scenarios.cs <- readRDS(file = here::here('data', 'scenarios.rds'))[1:9,]

# rename and only take columns we need -- no lambdas here
low.cs <- row.low.cs %>%
  dplyr::rename(phi1 = `mean.phi[1]`, phiad = `mean.phi[2]`) %>%
  dplyr::select(!starts_with('lambda'))

#check; same as above for non-case study, right?
#label scenarios 1:25, but only 10 taken below in inner_join()
low.params.cs <- readRDS(file = here::here('data', 'low.lam.params.rds')) %>%
  transform(scenario = 1:25)

#add in simscenario numbering to merge below
sim.scens.cs <- scenarios.cs %>%
  transform(simscenarios = 1:9) %>%
  dplyr::select(-c(lambda, n.viable.combinations))

#combine to get true values integrated in results; 
#only scenarios 1:10 out of 1:25 will be taken with inner_join
low.cs.dat <- low.cs %>%
  inner_join(low.params.cs, by = 'scenario', suffix = c('.obs', '.true')) %>%
  merge(sim.scens.cs) %>%
  transform(lambda.scenario = 'Decreasing')

```{r case study bias}

###case study for Euring poster:
# only a decreasing population trend, only 'L' nest detection

#get posterior medians
cs.meds <- low.cs.dat %>%
  dplyr::select('phi1.obs', 'phi1.true', 'phiad.obs', 'phiad.true', 'fec.obs', 'fec.true',
                            'sims', 'scenario', 'simscenarios', 'lambda.scenario') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'sims', 'scenario', 'simscenarios')) %>%
  group_by(lambda.scenario, scenario, simscenarios, variable) %>%
  summarize(median = median(value), .groups = 'keep') %>%
  reshape2::dcast(lambda.scenario + scenario + simscenarios ~ variable, value.var = 'median')

# bias
rel.bias.cs <- cs.meds %>%
  #calculate relative bias, mean across scenarios
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true) %>%
  dplyr::select('lambda.scenario', 'scenario', 'simscenarios', 
                'phi1.bias', 'phiad.bias', 'fec.bias') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'simscenarios')) %>%
  group_by(lambda.scenario, simscenarios, variable) %>%
  dplyr::summarize(mean.rel.bias = mean(value), .groups = 'keep') %>%
  transform(variable = factor(variable, levels = c('phiad.bias', 'phi1.bias', 'fec.bias'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity'))) %>% 
  merge(sim.scens.cs, by = 'simscenarios') %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H')),
            det.MR = factor(det.MR, levels = c('L', 'M', 'H')))

# plot; blrgh. Why don't these results change across detection levels?!
ggplot(rel.bias.cs, aes(x = factor(det.MR), y = variable, fill = mean.rel.bias)) +
  geom_tile(color = 'grey50') +
  xlab('MR detection') + ylab('') +
  facet_grid(~det.abund, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      mid = "#f7f7f7", low = "royalblue4", high = "orange1", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
  theme_minimal() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

##hmmm.... adult survival on it's own scale looks like what I would expect
ggplot(rel.bias.cs %>% filter(variable == 'Adult survival'), 
       aes(x = factor(det.MR), y = variable, fill = mean.rel.bias)) +
  geom_tile(color = 'grey50') +
  xlab('MR detection') + ylab('') +
  facet_grid(~det.abund, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
  theme_minimal() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

ggplot(rel.bias.cs %>% filter(variable == 'Juv survival'), 
       aes(x = factor(det.MR), y = variable, fill = mean.rel.bias)) +
  geom_tile(color = 'grey50') +
  xlab('MR detection') + ylab('') +
  facet_grid(~det.abund, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
  theme_minimal() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))
